---
title: "<i class='bi bi-calendar3'></i> Lecture slides and handouts"
---


::: .callout-note
Term 2 runs 8 January to 13 April. 
:::

::: {.callout-warning}
Schedule is on Canvas. All dates subject to change.
:::

```{r load-sched}
#| echo: FALSE
#| eval: FALSE
library(tibble)
tib <- readr::read_delim("_data/schedule.txt", "|", trim_ws = TRUE, na = "NA")
tib <- tib[ ,1:3]
```

```{r sched}
#| echo: FALSE
#| eval: FALSE
knitr::kable(tib)
```


## Lecture slides

* [Bootstrap](slides/bootstrap.qmd)
* [Cluster computing](slides/cluster-computing.qmd)
* [Git and GitHub](slides/git.qmd)
* [Skills for graduate students](slides/grad-school.qmd)
* [Tips for organization](slides/organization.qmd)
* [Giving presentations](slides/presentations.qmd)
* [Time series](slides/time-series.qmd)
* [Unit tests](slides/unit-tests.qmd)

## Handouts

* [Recommended books and sources](handouts/reference-books.qmd)
* [Formatting consulting reports](handouts/report-formatting.qmd)


<!--


## Guest lecturers

-->
